Universal Anonymous Signatures

### 2022-09-19 prism-backend/research/gsac/introduction-paper.tex
Minor changes.
Completed in-depth pass. Some changes pending.

The three functional placeholders mentioned above are \fissue, \feval, and
\finsp. \fissue is the function that users are required to evaluate at issuance
time, to prove knowledge of a user key and, potentially, claims over attributes
in previously obtained credentials. \feval is computed at signing time by the
user, and controls and proves correctness of the information learned by
verifiers. Finally, \finsp, although  computed also at signing time by the
users, proves correctness of the utility information extractable after signing.
The latter is, in addition, fed and modulated with the output of \feval. Through
these functions, we define NP statements that need to be proven by different
algorithms/protocols, summarised in \figref{fig:proof-blocks-uas}.

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.85}{
    \input{figures/relations.tex}
  }
  \caption{Summary of schemes that can be instantiated as restrictions of our
    generic constructions and proved secure under our \UAS model. Between
    parenthesis we show the adopted reference model, and the section offering
    full detail.}
  \label{fig:relations}
\end{figure}

>>>>

The three functional placeholders mentioned above are \fissue, \feval, and
\finsp. \fissue is the function that users are required to evaluate at issuance
time, to prove knowledge of a user key and, potentially, claims over attributes
in previously obtained credentials. \feval is computed at signing time by the
user, and controls and proves correctness of the information learned by
verifiers. Finally, \finsp, although  computed also at signing time by the
users, proves correctness of the utility information extractable after signing.
The latter is, in addition, fed and modulated with the output of \feval. With
these functions, we allow achieving configurable utility-vs-privacy tradeoffs
throughout the whole ``lifecycle'' (from issuance to opening). They also take
a central role in defining the NP statements that need to be proven by different
algorithms/protocols, summarised in \figref{fig:proof-blocks-uas}.

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.85}{
    \input{figures/relations.tex}
  }
  \caption{Summary of schemes that can be instantiated as restrictions of our
    generic constructions and proved secure under our \UAS model. Between
    parenthesis we show the adopted reference model, and the section offering
    full detail. \CUASGenInt and \CUASGenHideIss are variations of \CUASGen,
    described in \secref{sec:formal-uas}.}
  \label{fig:relations}
\end{figure}
